Influence of galaxy rotation and outflows in the Lyman Alpha spectral line

### 2017-03-02 paper/paper.tex
one plot missing

TERMINAR...\\
\end{abstract}

@@

\subsection{Parameters' Initial Values}
In order to define the ranges of \tauh, \vrot and \vout, it is necessary to refer to observational constraints. The common values for typical LAEs are in Tab. \ref{tab:values}. We run CLARA's modified version for all the permutations of these 3 parameters. \\

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/summary}
	\end{center}
	\caption{\textbf{4 different \lya profiles:} With \tauh$=10^5$ and $\theta \simeq 90^\circ$. The rotational velocity \vrot increases to the right and the outflows velocity \vout increases downwards. The intensity is in arbitrary units.
		\label{fig:summary}}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/influence_viewing_angle_5}
	\end{center}
	\caption{\textbf{\lya profile for different $\theta$:} With \tauh$=10^5$, \vrot$=50$ \kms and \vout$=20$ \kms.The intensity is in arbitrary units.
		\label{fig:influence_viewing_angle_5}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/influence_viewing_angle_6}
	\end{center}
	\caption{\textbf{\lya profile for different $\theta$:} With \tauh$=10^6$, \vrot$=100$ \kms and \vout$=5$ \kms.The intensity is in arbitrary units.
		\label{fig:influence_viewing_angle_6}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/influence_viewing_angle_7}
	\end{center}
	\caption{\textbf{\lya profile for different $\theta$:} With \tauh$=10^7$, \vrot$=100$ \kms and \vout$=15$ \kms.The intensity is in arbitrary units.
		\label{fig:influence_viewing_angle_7}}
\end{figure}

From Figs. \ref{fig:influence_viewing_angle_5}, \ref{fig:influence_viewing_angle_6} and \ref{fig:influence_viewing_angle_7} is clear that the intensity of the valley between the two peaks increases along with $\theta$. This causes an intensity decrease in the rest of the frequencies, thus a broadening of the line. The asymmetry also changes with the viewing angle.\\

>>>>

REVISAR AL FINAL...\\
\end{abstract}

@@

\subsection{Resulting simulated spectra}
In order to define the ranges of \tauh, \vrot and \vout, it is necessary to refer to observational constraints. The common values for typical LAEs that were set as parameters are in Tab. \ref{tab:values}. We run CLARA's modified version for all the permutations of these 3 parameters. \\

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/summary}
	\end{center}
	\caption{\textbf{4 different \lya profiles:} With \tauh$=10^5$ and $\theta \simeq 90^\circ$. The rotational velocity \vrot increases to the right and the outflows velocity \vout increases downwards. The intensity is in arbitrary units.
		\label{fig:summary}}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{./figures/angles}
	\end{center}
	\caption{\textbf{\lya profile for different $\theta$.} For \tauh$=10^5$, \vrot$=50$ \kms and \vout$=20$ \kms. For \tauh$=10^6$, \vrot$=100$ \kms and \vout$=5$ \kms. For \tauh$=10^7$, \vrot$=100$ \kms and \vout$=15$ \kms. The intensity is in arbitrary units.
		\label{fig:angles}}
\end{figure}

From Fig. \ref{fig:angles} it is clear that the intensity of the valley between the two peaks increases along with $\theta$. This causes an intensity decrease in the rest of the frequencies, thus a broadening of the line. The asymmetry also changes with the viewing angle.\\
